Usage metrics

### 2021-03-04 analysis/expressions.Rmd
Generate separate tag files and names for each dataset

source("inc/paths.R")
source("inc/latextags.R")
source("inc/functions.R")
theme_set(theme_minimal())
create_tags(path(TAGS_DIR, "usage_metrics.tex"), prefix = "", default = TRUE)

>>>>

source("inc/paths.R")
source("inc/latextags.R")
source("inc/functions.R")
theme_set(theme_minimal())

dataset_name <- basename(params$base_dir)
create_tags(path(TAGS_DIR, paste0(dataset_name, "_expressions.tex")), prefix = dataset_name, default = TRUE)

### 2021-03-04 analysis/normalized.Rmd
Generate separate tag files and names for each dataset

source("inc/paths.R")
source("inc/latextags.R")
source("inc/functions.R")
theme_set(theme_minimal())
create_tags(path(TAGS_DIR, "usage_metrics.tex"), prefix = "", default = TRUE)

>>>>

source("inc/paths.R")
source("inc/latextags.R")
source("inc/functions.R")
theme_set(theme_minimal())

dataset_name <- basename(params$base_dir)

# Tags will be prefixed by the dataset name
create_tags(path(TAGS_DIR, paste0(dataset_name, "_normalized_expr.tex")), prefix = dataset_name, default = TRUE)

### 2021-03-04 analysis/usage.Rmd
Generate separate tag files and names for each dataset

---
title: "Usage metrics"
author: "Pierre Donat-Bouillud"
output:
    html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: Data/package/
  calls_path: summarized.fst
  corpus_path: ../corpus.fst
  static_path: evals-static.csv
  force_rebuild: TRUE
---

@@

source("inc/paths.R")
source("inc/latextags.R")
source("inc/functions.R")
theme_set(theme_minimal())
create_tags(path(TAGS_DIR, "usage_metrics.tex"), prefix = "", default = TRUE)

calls_path <- paste0(params$base_dir, params$calls_path)
corpus_path <- paste0(params$base_dir, params$corpus_path)
static_path <- paste0(params$base_dir, params$static_path)
```

@@

rebuild <- TRUE
# We only read the file if we don't have our summarized file on disk.
# To force reading, set the force_rebuild parameter to true.
if (file.exists("Data/.lock.fst")) {
  saved <- read.fst("Data/.lock.fst")[[1,1]]
  if (saved == file.size(calls_path)) {
    read.fst("Data/E.fst") %>% as_tibble() -> E
    rebuild <- FALSE
  }
}
if (params$force_rebuild | rebuild) {
  read_fst(calls_path) %>% as_tibble() -> E_raw

  E_raw %>% select(
    run_package = package, #      The package which was run to trigger the eval
    ev_variant = eval_function, # Which eval variant was called
    duplicates = nb_ev_calls, #   Number of identical eval calls (weight)
    src_ref = eval_call_srcref, # Source ref for the eval call site
    file, #                       Script file name (name of this run)
    ev_package = eval_source, #   Package of the call site
    arg_size = expr_resolved_length, #   Size in characters of argument 
    ast_nodes = expr_resolved_nodes, #   Size in AST Nodes
    type = expr_resolved_type_tag,   #   Argument type
    opcodes = interp_eval #  Count of the AST nodes traversed by the
  ) %>% #                                interpreter during eval (non-recursive).
   mutate(across(where(is_character),as_factor)) -> E 
  write.fst(E, "Data/E.fst")
  sz <- file.size(calls_path) %>% as_tibble()
  write.fst(sz,"Data/.lock.fst")
}

@@

```{r exercised-vs-static, include=FALSE}
stat_evl <- P %>% filter(call_fun_name == "eval")        %>% nrow()
stat_evq <- P %>% filter(call_fun_name == "evalq")       %>% nrow()
stat_evp <- P %>% filter(call_fun_name == "eval.parent") %>% nrow()
stat_loc <- P %>% filter(call_fun_name == "local")       %>% nrow()

@@

ggplot2_symbs <- E %>% filter(ev_package == "ggplot2") %>% 
  count(type, wt=duplicates) %>% filter(type == "symbol") %>% .$n

>>>>

---
title: "Usage metrics"
author: "Pierre Donat-Bouillud"
output:
    html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: Data/kaggle/
  calls_path: summarized.fst
  corpus_path: ../corpus.fst
  static_path: evals-static.csv
  force_rebuild: TRUE
---

@@

source("inc/paths.R")
source("inc/latextags.R")
source("inc/functions.R")
theme_set(theme_minimal())

dataset_name <- basename(params$base_dir)
create_tags(path(TAGS_DIR, paste0(dataset_name, "_usage_metrics.tex")), prefix = dataset_name, default = TRUE)

calls_path <- paste0(params$base_dir, params$calls_path)
corpus_path <- paste0(params$base_dir, params$corpus_path)
static_path <- paste0(params$base_dir, params$static_path)

lock_path <- paste0(params$base_dir, ".lock.fst")
min_path <- paste0(params$base_dir, "E.fst")
```

@@

rebuild <- TRUE
# We only read the file if we don't have our summarized file on disk.
# To force reading, set the force_rebuild parameter to true.
if (file.exists(lock_path)) {
  saved <- read.fst(lock_path)[[1,1]]
  if (saved == file.size(calls_path)) {
    read.fst(min_path) %>% as_tibble() -> E
    rebuild <- FALSE
  }
}
if (params$force_rebuild | rebuild) {
  read_fst(calls_path) %>% as_tibble() -> E_raw

  E_raw %>% select(
    run_package = package, #      The package which was run to trigger the eval
    ev_variant = eval_function, # Which eval variant was called
    duplicates = nb_ev_calls, #   Number of identical eval calls (weight)
    src_ref = eval_call_srcref, # Source ref for the eval call site
    file, #                       Script file name (name of this run)
    ev_package = eval_source, #   Package of the call site
    arg_size = expr_resolved_length, #   Size in characters of argument 
    ast_nodes = expr_resolved_nodes, #   Size in AST Nodes
    type = expr_resolved_type_tag,   #   Argument type
    opcodes = interp_eval #  Count of the AST nodes traversed by the
  ) %>% #                                interpreter during eval (non-recursive).
   mutate(across(where(is_character),as_factor)) -> E 
  write.fst(E, min_path)
  sz <- file.size(calls_path) %>% as_tibble()
  write.fst(sz, lock_path)
}

@@

```{r exercised-vs-static, include=FALSE}
# stat_evl <- P %>% filter(call_fun_name == "eval")        %>% nrow()
stat_evq <- P %>% filter(call_fun_name == "evalq")       %>% nrow()
stat_evp <- P %>% filter(call_fun_name == "eval.parent") %>% nrow()
stat_loc <- P %>% filter(call_fun_name == "local")       %>% nrow()

@@

ggplot2_symbs <- E %>% filter(ev_package == "ggplot2")

# For Kaggle, there are not eval calls originating from ggplot2
ggplot2_symbs <- if(nrow(ggplot2_symbs) == 0 ) {
  0 
} else {
  ggplot2_symbs %>% count(type, wt=duplicates) %>% filter(type == "symbol") %>% .$n
}
